Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-05 paper/ijcai/paper.tex
pass on section 3

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest.  Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
  static
  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\comments{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
slices that are executable.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation. The
Lithium minimization process starts by determining the initial size of
chunks---in number of lines---to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere~\cite{lithium-complexity}. Our implementation is publicly
available.

@@

To illustrate the \sfl{}+slicing combination, consider a debugging
scenario with five components $c_{1..5}$ and five transactions
$t_{1..5}$, two of which are failing. Consider additionally that the
component $c_2$ is faulty.  Figure~\ref{fig:illustration} shows, at
the left-hand side of the arrow ($\Rightarrow$), the spectra for this
scenario and its corresponding ranking, produced with the Ochiai
predictor. Each line in the ranking shows the ranking position, the
label of the component, and the Ochiai score (in parentheses). The
spectra and ranking appearing at the right-side of the arrow are
obtained with the \sfl{}+slicing combination, assuming that the slice
for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
enables identification of cells in the spectra whose values can be set
to zero, \ie{}, the components marked with 0 are irrelevant to
determine the test output. Let us now observe the impact of this
change at the ranking. Analyzing the Ochiai formula, one can observe
that, for the statements $j$ which are not part of the slice of a
failing test, the combination reduces the value of $\N{11}$ and
increases the value of $\N{01}$. Therefore, suspiciosness of those
statements decrease. Similar argument applies to other fault
predictors. In the example from Figure~\ref{fig:illustration},
components $c_3$ and $c_4$, which are not in the slice of $t_2$, have
their suspiciousness reduced, enabling the faulty component $c_2$ to
rise from the third to the first position in the ranking.

@@

  \caption{Modifications on spectra and ranking as result of slicing
    code against test $t_2$. Double arrow ($\Rightarrow$) indicates
    before and after.}
  \label{fig:illustration}
\end{figure}

---- estou aqui -Marcelo

\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
following steps: (1) Compute the execution spectra as discussed in
Section~\ref{sec:sfl}, (2) Compute slices associated with failing
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores.

>>>>

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest.  Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
  static
  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\comments{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere~\cite{lithium-complexity}. Our implementation is publicly
available.

@@

The \sfl{}+\cs{} combination consists of four steps:
\begin{enumerate}
  \itemsep0em 
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
  \item Select top $k$ most suspicious source files, according to $R$;
  \item\label{step:compute-slice} Compute slices for every $k$;
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the results obtained in Step~\ref{step:compute-slice} and recompute ranking;
\end{enumerate}

\Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
  falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
  de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
  loop aninhado ao loop ``for every k'' que o lithium-slicer
  implementa (algo como ``for every k and every failing test'')?  Caso
  vc. faca slice contra um teste particular, vc. garante (checa saida)
  que os demais testes que originalmente falhavam continuam falhando
  pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
  de inicio.}

To illustrate the \sfl{}+\cs{} combination, consider a debugging
scenario with five components $c_{1..5}$ and five transactions
$t_{1..5}$, two of which are failing. Consider additionally that the
component $c_2$ is faulty.  Figure~\ref{fig:illustration} shows, at
the left-hand side of the arrow ($\Rightarrow$), the spectra for this
scenario and its corresponding ranking, produced with the Ochiai
predictor. Each line in the ranking shows the ranking position, the
label of the component, and the Ochiai score (in parentheses). The
spectra and ranking appearing at the right-side of the arrow are
obtained with the \sfl{}+\cs{} combination, assuming that the slice
for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
enables identification of cells in the spectra whose values can be set
to zero, \ie{}, the components marked with 0 are irrelevant to
determine the test output. Let us now observe the impact of this
change at the ranking. Analyzing the Ochiai formula, one can observe
that, for the components $j$ which are not part of the slice of a
failing test, the combination reduces the value of $\N{11}$ and
increases the value of $\N{01}$. Therefore, suspiciosness of those
components decrease. Similar argument applies to other fault
predictors. In the example from Figure~\ref{fig:illustration},
components $c_3$ and $c_4$, which are not in the slice of $t_2$, have
their suspiciousness reduced, enabling the faulty component $c_2$ to
rise from the third to the first position in the ranking.

@@

  \caption{Modifications on spectra and ranking as result of slicing
    code against test $t_2$. Double arrow ($\Rightarrow$) indicates
    before and after.}
  \label{fig:illustration}
  \vspace{-2ex}
\end{figure}

\Mar{.....parei aqui}
